% Created 2015-06-17 Wed 13:52
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\tolerance=1000
\usepackage[utf8]{inputenc}
\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault}
\author{Oleg Sivokon}
\date{\textit{<2015-05-19 Tue>}}
\title{Resume}
\hypersetup{
 pdfauthor={Oleg Sivokon},
 pdftitle={Resume},
 pdfkeywords={Resume, job, employment, cv},
 pdfsubject={My resume},
 pdfcreator={Emacs 25.0.50.1 (Org mode 8.3beta)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Contact Information}
\label{sec:orgheadline1}
\begin{center}
\begin{tabular}{ll}
Name: & Oleg Sivokon\\
Birth date: & 23, 06, 1978\\
Cell phone: & +972 (0) 544-563314\\
Email: & \href{mailto:olegsivokon@gmail.com}{olegsivokon@gmail.com}\\
Address: & Florentin 50, Tel Aviv, Israel\\
\end{tabular}
\end{center}

\emph{You can find an up-to-date electronic copy of this document at}

\url{https://github.com/wvxvw/resume}

\clearpage

\section{Work History}
\label{sec:orgheadline6}

\subsection{PowToon Ltd.}
\label{sec:orgheadline2}
\begin{description}
\item[{What PowToon does}] PowToon is a software as service kind of start-up
which specializes in presentation software.
\item[{What I did there}] I worked as a programmer.
\begin{itemize}
\item Relevant
\begin{itemize}
\item I wrote and maintained build scripts in Ant and Gradle.
\item I wrote tests using Selenium server.
\item I managed Jenkins continuous integration server.
\end{itemize}
\item Irrelevant
\begin{itemize}
\item I wrote a SWF format encoder (using Haxe programming language).
\item I wrote several scripts to extract some statistics from the company's
user database related to customers' sentiment analysis.
\end{itemize}
\end{itemize}

\item[{When did I do it}] January 2014--May 2015
\end{description}

\subsection{TransGaming Inc.}
\label{sec:orgheadline3}
\begin{description}
\item[{What TransGaming does}] TransGaming is a game development company which
specializes in embedded software, ``smart'' television in particular.
\item[{What I did there}] I worked as a programmer.
\begin{itemize}
\item Relevant
\begin{itemize}
\item I wrote number of tests for Selenium server (using Python programming
language).
\item I wrote a player AI which played the games in order to test their
performance.
\end{itemize}
\item Irrelevant
\begin{itemize}
\item I wrote a game portal (using TypeScript programming language).
\item I re-wrote a Luxor game to be used for testing and bench-marking
on television sets supporting WebKit, Presto or Geko (using JavaScript
programming language).
\end{itemize}
\end{itemize}

\item[{When did I do it}] April 2013--2013 (less than a year)
\end{description}

\subsection{Rounds}
\label{sec:orgheadline4}
\begin{description}
\item[{What Rounds does}] Rounds develops a video chat. Their product is available
in a number of ways, such as through a web client interface or a mobile
phone app.
\item[{What I did there}] I worked as a programmer.
\begin{itemize}
\item Relevant
\begin{itemize}
\item I wrote a mock server in order to leverage functional testing for the
client-server interaction (using Python programming language).
\item I wrote a test chat client (using Erlang programming language).
\end{itemize}
\item Irrelevant
\begin{itemize}
\item I wrote the communication part of the client (using ActionScript
programming language).
\end{itemize}
\end{itemize}

\item[{When did I do it}] December 2010 – August 2011 (9 months)
\end{description}

\subsection{Other Jobs}
\label{sec:orgheadline5}
\begin{description}
\item[{HP (Hewlett Packard)}] I worked for almost a year in HP office in Yehud.
during this time I worked on a Flex front-end for a large accounting
application.  I also wrote some Java code related to client-server
communication.
\item[{Mishloha}] I worked there very briefly.  The company was hoping to transition
their old infrastructure written in ASP Classic (both VB and JScript) to
Ruby on Rails, but they gave up their project.  They also had a sizable
amount of code written in PHP.  My job there mostly included a failed
attempt at cleaning up the layers of cruft left by bygone developers.
\item[{Zibaba}] I freelanced there preparing the site for i18n.
\item[{AdItAll}] AdItAll is a SaaS company which provides video editing tools for
amateurs.  I've worked on the client side of the project.
\item[{Gazit Studio}] My first programming job in a small shop, which develops
personal and small-business web-sites.  I worked on the client-side.
\end{description}

\section{Frequently Asked Questions}
\label{sec:orgheadline7}
\begin{description}
\item[{Q}] Am I familiar with web stack (HTML, CSS, JavaScript)?
\item[{A}] Yes, but I prefer to do something else for living.

\item[{Q}] Most of my experience indicates I worked on client side, why do I want
to switch to development and operations or Python?
\item[{A}] Client-side development, historically, was always left to the armature
programmers.  It uses technologies which don't require any skill or
knowledge on the part of the programmer.  On top of it, the programs are
not judged by their programming merits, but mostly rely on the subjective
``feeling'', based primarily on the work of the graphic designer.

\item[{Q}] How many programming languages do I know? Please give us a list.
\item[{A}] I certainly know more than you do.  An exhaustive list would bore you
to death with the names you don't know how to read.  It's easier to
tell which languages I consciously tried to avoid.
\begin{itemize}
\item I don't like C++.  It's an over-marketed very poorly designed language.
\item I will not write in C\#, because writing in C\# implies working on MS Windows,
and that's just immoral.  I've sinned enough already, I'm not looking to
cooperate with more corrupt enterprises on top of it.  The argument,
of course, extends to the entire .NET platform as well as Obj-C, and other
such monsters.
\item I don't know Pascal.  Everyone since the don of the programming era seems
to be happy writing pseudo-code in broken likelihood of Pascal.  This is
something I can't stand about this language.  Use FORTRAN, motherlovers,
be authentic!
\end{itemize}

\item[{Q}] Do I have any Linux experience?
\item[{A}] The answer should be obvious by now, but if it isn't, then here it is:
Yes.

\item[{Q}] Do I know any SQL?
\item[{A}] Yes I do.

\item[{Q}] And NoSQL?
\item[{A}] Yes, quite a lot, actually.
\end{description}

\section{Courses}
\label{sec:orgheadline8}
I took several online courses from Coursera, Udacity and edX, which required
me to complete programming assignments in Python.

I took a complete series of courses in statistics at edX (three courses),
the data scientist toolbox course at Coursera (six short courses), machine
learning at Udacity, introduction to algorithms (two courses) at Coursera.

I also volunteered for SCons project, writing an ActionScript plugin for it.
(SCons is an extensible build system written in Python).

Two years ago I interviewed for a position of Python programmer at Walla.
They requested that I write a small test project, which I did.  The project,
although somewhat outdated, is still available for viewing:
\url{https://github.com/wvxvw/intj}.

I am currently studying in Open University of Israel, mathematics faculty,
about to finish my first year.

\section{Hobbies}
\label{sec:orgheadline9}
\begin{itemize}
\item NLP
\item Computational linguistics
\item Moral philosophy
\item General AI
\item Graphs
\end{itemize}
\end{document}