% Created 2015-04-27 Mon 14:47
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage[utf8]{inputenc}
\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault}
\author{Oleg Sivokon}
\date{\textit{<2014-11-28-Fri>}}
\title{Resume}
\hypersetup{
  pdfkeywords={Resume, job, employment, cv},
  pdfsubject={My resume},
  pdfcreator={Emacs 25.0.50.1 (Org mode 8.2.2)}}
\begin{document}

\maketitle

\clearpage
\thispagestyle{plain}
% \hspace{4cm}
\vspace*{9cm}{
  {\fontfamily{ugq}\selectfont
    {\Huge Dear} human resources specialist!

    I am looking for a {\Huge Python} job.

    {\Huge Thank you} for understanding.}}
\clearpage

\section{Foreword}
\label{sec-1}
Even though most of my recorded experience is in Flash and associated
technologies, I am now looking to continue in a different field.  Being an
Emacs user, my preferences of language, operating system and general attitude
towards my trade have grown to be very different from those typical of the
Flash community.  The closest thing I can possibly hope to find on the jobs
market would be a Python programmer position, with a very strong preference
towards Linux as a working environment.

I have so far used Python to write integration tests for the programs I
wrote in other languages.  Most of that code was written to work with Selenium
server.  I also wrote an in-house system for test case submission and generation
as well as performance testing.

I also used Python to write build scripts.  I've extended SCons to build Flash
projects.  I also used Fabric to automate some deployment processes.

I learned Python mostly on my own, however I also took courses in
machine-learning and statistics which required familiarity with the language.
During the courses I become familiar with NumPy, SciPy, Pandas as well as
touched a bit on Cython.

I used Tornado server in a test assignment I completed for another employer,
which you can find here: \url{https://github.com/wvxvw/intj}
\section{Work History}
\label{sec-2}

\subsection{PowToon Ltd.}
\label{sec-2-1}
\begin{itemize}
\item \textbf{Position:} \emph{Programmer}
\item \textbf{Term:} \emph{January 2014 – Present}
\end{itemize}
\subsection{TransGaming Inc.}
\label{sec-2-2}
\begin{itemize}
\item \textbf{Position:} \emph{Programmer}
\item \textbf{Term:} \emph{April 2013 – 2013 (less than a year)}
\end{itemize}
\subsection{Hewlett-Packard}
\label{sec-2-3}
\begin{itemize}
\item \textbf{Position:} \emph{Programmer}
\item \textbf{Term:} \emph{October 2011 – April 2012 (7 months)}
\end{itemize}
\subsection{Rounds}
\label{sec-2-4}
\begin{itemize}
\item \textbf{Position:} \emph{Programmer}
\item \textbf{Term:} \emph{December 2010 – August 2011 (9 months)}
\end{itemize}
\subsection{BrainPOP}
\label{sec-2-5}
\begin{itemize}
\item \textbf{Position:} \emph{Advisor}
\item \textbf{Term:} \emph{2008 – March 2010 (2 years)}
\end{itemize}
\subsection{AditAll}
\label{sec-2-6}
\begin{itemize}
\item \textbf{Position:} \emph{Programmer}
\item \textbf{Term:} \emph{June 2007--March 2010 (2 years 10 months)}
\end{itemize}
\subsection{Gazit Studio}
\label{sec-2-7}
\begin{itemize}
\item \textbf{Position:} \emph{Programmer}
\item \textbf{Term:} \emph{January 2006--June 2006 (6 months)}
\end{itemize}
\subsection{TimeZero LLC}
\label{sec-2-8}
\begin{itemize}
\item \textbf{Position:} \emph{Designer}
\item \textbf{Term:} \emph{June 2005 – December 2005 (7 months)}
\end{itemize}
\section{Skills}
\label{sec-3}
Listed below are the languages I used to write something more substantial
than a ``hello world'' program, but my level of proficiency with them is
very different.  My favorite languages are in the Lisp family, but I also
like Prolog and am interested in statistical programming.

\subsection{Lisps}
\label{sec-3-1}
\begin{itemize}
\item Common Lisp
\item Scheme
\item Clojure
\item Shen
\item JavaScript
\item ActionScript
\end{itemize}
\subsection{Fortran Family}
\label{sec-3-2}
\begin{itemize}
\item Java
\item C
\item C\#
\end{itemize}
\subsection{ML Family}
\label{sec-3-3}
\begin{itemize}
\item OCaml
\item Haskell
\item Erlang
\item Haxe
\item Scala
\end{itemize}
\subsection{Basic Family}
\label{sec-3-4}
\begin{itemize}
\item Python
\end{itemize}
\subsection{Math and Statistics}
\label{sec-3-5}
\begin{itemize}
\item Octave (Matlab)
\item R (S)
\item Maxima
\item J
\end{itemize}
\subsection{Logic Programming}
\label{sec-3-6}
\begin{itemize}
\item Prolog
\item Mercury
\end{itemize}
\subsection{Misc}
\label{sec-3-7}
\begin{itemize}
\item Rust
\item SQL
\item Forth
\end{itemize}
\subsection{DevOps}
\label{sec-3-8}
\begin{itemize}
\item Shell
\item General familiarity with Jenkins.
\item Gradle
\item SCons
\item Ant
\item Grunt
\end{itemize}
\section{Hobbies}
\label{sec-4}
\begin{itemize}
\item NLP
\item Computational linguistics
\item Moral philosophy
\item General AI
\item Graphs
\end{itemize}
% Emacs 25.0.50.1 (Org mode 8.2.2)
\end{document}