% Created 2021-06-02 Wed 21:02
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[scaled]{helvet}
\usepackage[a4paper, total={7in, 9in}]{geometry}
\renewcommand*\familydefault{\sfdefault}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta,urlcolor=cyan}
\urlstyle{same}
\author{Oleg Sivokon}
\date{\textit{<2019-07-24 Wed>}}
\title{}
\hypersetup{
 pdfauthor={Oleg Sivokon},
 pdftitle={},
 pdfkeywords={Resume, job, employment, cv},
 pdfsubject={My resume},
 pdfcreator={Emacs 26.3 (Org mode 9.1.9)}, 
 pdflang={English}}
\begin{document}

\begin{center}
Oleg Sivokon

Born June 23, 1978

+972 (0) 544-563314

\url{mailto:olegsivokon@gmail.com}

Byalik 152, Apt. 16, Ramat Gan, Israel \\[18pt]

\small \emph{You can find an up-to-date electronic resume at}

\url{https://github.com/wvxvw/resume} \\[48pt]
\end{center}

\section*{Technology Skills}
\label{sec:org3c97984}
My latest employer, Replix.IO, develops a storage product,
specifically, a long-distance online zero-RTO (Recovery Time
Objective) replication software.  The product evolved and so did the
company.  It started as an on-premise installation product and
transormed into a service offered through public cloud providers
such as AWS, Azure or GCP.  Today, the product is offered as a CSI
plugin for Kubernetes.  The product utilizes a lot of modern
technologies, Docker, Kubernetes, SPDK, Prometheus, Terraform, among
others.

The core of the product is written in Rust, the Kubernetes-facing
part is written in Go, but automation code is almost entirely
written in Python.

Automation tools rely on ZMQ for communication, Behave for test
harness.  We've developed a test deployment tool in-house to extends
Wheel format for Python packages in order to deploy the tests.

We use some third-party testing tools s.a. SysBench and DBT2 in our
tests as well as a lot of usual Linux tooling, like FIO, SAR, and
tools that come with popular storage products like \texttt{pgbench} and
\texttt{cassandra-stress}.

\subsection*{Previous experience}
\label{sec:org9f75cdb}
Before working for Replix.IO, I worked with another storage
product: Elastifile distributed file system (created by
Elastifile).  I worked on a large infrastructure project mostly
written in Go, which used some popular third-party tools for
testing, FIO, FSF2008, FSF2012, VDBench among others.  Since this
was before Docker Swarm, while Kubernetes was in its infancy, a lot
of infrastructure code was dedicated to container management.

Another part of this project was about integration with VMWare's
VCenter, which was considered the primary target for the product.

\subsection*{Non-work-related (programming) skills}
\label{sec:orga03ed75}
I like Lisp and Prolog.  I have decent knowledge of Common Lisp.
I'm very enthusiastic about Mercury.  I know Emacs Lisp fairly
well.  I help my wife with statistical programming in Python using
Pandas, Pill and other popular data-science software.

\section*{Work History}
\label{sec:org66e1213}

\subsection*{Replix.IO}
\label{sec:org03bc47a}
\begin{description}
\item[{Programmer}] August 2018--present
\begin{itemize}
\item Wrote tools for automating company's product testing as well as
automating development process.
\end{itemize}
\end{description}

\subsection*{NEX Traiana}
\label{sec:org2b7cd1a}
\begin{description}
\item[{Programmer}] August 2017--August 2018
\begin{itemize}
\item Wrote tools for automating microservice deployment, debugging
and testing.
\end{itemize}
\end{description}

\subsection*{AllAspect}
\label{sec:org8c8d6be}
\begin{description}
\item[{Programmer}] April 2017--August 2017
\begin{itemize}
\item Wrote tools for automatic trading in digital media market.
\item Wrote tools for reporting, representing and processing of
statistical data.
\end{itemize}
\end{description}

\subsection*{Elastifile}
\label{sec:org1ab5aca}
\begin{description}
\item[{Programmer}] December 2015--April 2017
\begin{itemize}
\item Rewrote the build system of the infrastructure part of the
project.
\item Wrote NFS client for testing the company's product.
\item Wrote ``glue'' code that allowed automated testing code to
interface with system code.
\end{itemize}
\end{description}

\subsection*{PowToon Ltd.}
\label{sec:orgbf4c069}
\begin{description}
\item[{Programmer}] January 2014--May 2015
\begin{itemize}
\item Rewrote the major application component (the player).
\item Wrote most of the infrastructure code such as build scripts,
automated test generation and continuous integration server
setup.
\item Wrote several designs for the product.
\end{itemize}
\end{description}

\subsection*{TransGaming Inc.}
\label{sec:org5f27731}
\begin{description}
\item[{Programmer}] April 2013--2013
\begin{itemize}
\item Wrote a game portal for ``Smart TV'' deployment.
\item Wrote a tester program, which stress-tested the program
performance on ``Smart TV''.
\item Wrote automated build for my project.
\item Wrote a sizable chunk of code dealing with usage statistic
aggregation using Google Analytics.
\end{itemize}
\end{description}

\subsection*{Rounds}
\label{sec:org0c41e5b}
\begin{description}
\item[{Programmer}] December 2010--August 2011
\begin{itemize}
\item Rewrote the communication part of the video chat application.
\item Wrote a testing server and utility programs for automated
testing.
\item Wrote a natural language processing program which was used
to advertise the company's product.
\end{itemize}
\end{description}

\section*{Education}
\label{sec:orge29bc54}
\begin{description}
\item[{Ukrainian Academy of Printing}] Lviv, Ukraine, 1995-1999.  Fine
and Applied Art.  At the time, UAoP did not offer a batchelors
degree.  I did not complete masters degree, however.
\item[{Bezalel Academy of Art and Design}] Jerusalem, Israel, 2000-2002.
Visual Communication.  I attempted to transfer from UAoP, but
since Bezalel at the time did not offer masters degree,
eventually, I dropped out, as my goal was a terminatory degree.
\item[{Open University of Israel}] No campus, 2014-2018.  Joint
Mathematics and Computer Science program.  This university is
for full-time workers, designed to study remotely or in the
evening hours.  Technically, I'm still a student there, but I
did not sign up for any course in a few years.
\end{description}
\section*{University Level Courses}
\label{sec:org5b3c00d}
Data Scientist's Toolbox (statistics in R), Statistics, Data
Analysis, Machine Learning, Artificial Intelligence.

\section*{Volunteering And Community Work}
\label{sec:org40dc152}
SCons project, ActionScript plugin.  (SCons is an extensible build system
written in Python).

For several years I was a member of Adobe Community Board. I moderated a forum
dedicated to Flash and ActionScript as well as writing some articles such as
this one: \url{http://kb2.adobe.com/community/publishing/526/cpsid\_52670.html}

I'm an active member of Emacs Q\&A site from the StackExchange family.

\section*{Examples Of My Work}
\label{sec:orgb3bfb47}
My Github profile:
\begin{itemize}
\item \url{https://github.com/wvxvw/}.
\end{itemize}

\section*{Languages}
\label{sec:org0af72b4}
Fluent in English, Hebrew, Russian.

\section*{Hobbies}
\label{sec:org4293289}
NLP, Computational linguistics, Moral philosophy, General AI, Graphs.

\section*{Citizenship and Mobility}
\label{sec:org54fcc7e}
Citizen of Israel and Ukraine.  USA citizenship pending.  Willing
to relocate.
\end{document}
